\begin{itemize}
\item Previous studies have used packages that implement the same basic algorithm with extra features such as ways for setting priors, the shape of the production function and heuristics for depletion. They have shown that the choices made are essential to get a good estimate of depletion in the final year \citep{rosenberg2014developing}. However, even for data rich stocks productivity depends on difficult to estimate parameters such as the steepness of the stock recruitment relationship and natural mortality.  
\item A problem is how to make an objective choice between alternative COM runs when conducting sensitivity tests since diagnostics such as goodness of fit based on residuals, retrospective analysis and cross-validation are not applicable.
\item We used a variety of stocks, regions and fisheries, however in many cases stock from a limited region are used to derive heuristics. However, as we showed heuristics had more impact than the data. A better alternative may be to use an indicator stock or fishery
\item We used an assessment method that has been used to provide advice on stock status relative to target and limit reference points and to set quotas for data rich stocks. This allowed us to evaluate the impact of the different data types, assumptions, knowledge and priors on advice. 
\item We used ROC to compare the ability of methods to both rank and categorise stocks.
\item COMs cannot be used for management, which requires monitoring the effectiveness of regulations, since to fit a COM this must already be known. Fisheries independent data is important to provide a robust assessment of stock status, as the data used to set catch are the same as the management regulation then it is unlikely that COMs can provide robust estimates.    
\item Or to combine indicators into a empirical rule that can be tested using MSE \citep{fischer2020hcr}.
\end{itemize}


%A problem is that BMSY is not available for ICES assessments, instead, an approximation was used based on BLIM, which is an empirical quantity intended for management not a property of the dynamics. Therefore, using 3BLIM as a proxy for BMSY means that the references levels are biased and will be approximated by a Schaeffer production function as used in the COMs. This is unlikely to be correct, however, for the variety of life histories and dynamics represented by the ICES stocks.  Despite this, the COMs performed poorly. 

%The next problem is that ICES stocks have been managed by an MSY approach since [2008], this means that the heuristics are inappropriate and it is difficult to generalise results to stocks from other regions. This because the example stocks recovered and catch declining in the recent period, which unlikely to be the case in other regions. The scenarios evaluated use data are from the left-hand limb of the production function but in stocks for which COMs will be applied then datasets, data will be from the right-hand limb.
