---
title: "FAO VoI" 
subtitle: "Datasets"
author: "Laurence Kell"
output: rmarkdown:::html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---
  
```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =TRUE,
               cache.path="cache/data/",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =10,
               fig.path  ="../tex/figs/data-",
               dev       ="png")

options(digits=3)

iFig=0
```

```{r, pkgs, echo=FALSE, message=FALSE}
library(reshape)
library(plyr)
library(dplyr)
library(ggplot2)
library(GGally)
library(kobe)

library(diags)
library(r4ss)

library(FLCore)
library(FLife)
library(popbio)
library(mydas)
```

```{r, dirs, echo=FALSE, message=FALSE}
dirMy ="/home/laurence-kell/Desktop/papers/COM"
dirInp=file.path(dirMy,"inputs") 
dirDat=file.path(dirMy,"data")
dirRes=file.path(dirMy,"results")

source('~/Desktop/flr/diags/R/ss-prd.R')
source('~/Desktop/flr/kobe/R/kobe-generics.R')
source('~/Desktop/flr/kobe/R/fao-phaseMar.R')
source('~/Desktop/flr/kobe/R/fao-phase.R')
```


```{r, data, echo=FALSE, message=FALSE}
## Myers database
load(file.path(dirDat,"DBdata.RData"))
stockid=stock
names(stockid)[3]="species" 
save(stockid,file=file.path(dirDat,"stockid.RData"))
```

```{r, key}
key=c("B","Biomass; may be either total biomass or spawning stock biomass",
      "Bmgt"," Biomass at management target reference point",
      "Bmsy"," Biomass at MSY",
      "Cadv"," Scientifically advised catch",
      "CdivMSY","Catch divided by MSY",
      "Cpair","Catch corresponding to TAC and Cadv",
      "CPUE"," Catch per unit effort",
      "EFFORT","Measure of fishing effort (depends on fishery)",
      "ER","Exploitation rate (annual proportion)",
      "F","Fishing mortality (instantaneous rate)",
      "MSY","Maximum Sustainable Yield",
      "RecC","Recreational catch",
      "SSB","Spawning stock biomass",
      "survB","Survey biomass",
      "TAC","Total allowable catch",
      "TB","Total biomass",
      "TC","Total catch",
      "TL","Total landings",
      "TN","Total abundance; in numbers",
      "U","Harvest rate; may be either exploitation rate or fishing mortality",
      "Umsy","Harvest rate at MSY",
      "Umgt","Harvest rate at management target reference point")
nms=key[seq(2,44,2)]
names(nms)=key[seq(1,44,2)]

bbmsy =c("SSBdivSSBmsy-dimensionless",
         "SSBdivSSBmsy-calc-dimensionless",
         "TBdivTBmsy-dimensionless",
         "TBdivTBmsy-calc-dimensionless",
         "TNdivTNmsy-calc-dimensionless",
         "SSBdivSSBmgt-dimensionless",
         "SSBdivSSBmgt-calc-dimensionless",
         "TBdivTBmgt-dimensionless",
         "TBdivTBmgt-calc-dimensionless",
         "SSBdivSSBmsy-conv-dimensionless",
         "TBdivTBmsy-conv-dimensionless",
         "SSBdivSSBmsy-est-dimensionless",
         "TBdivTBmsy-est-dimensionless")

ffmsy =c("ERdivERmsy-dimensionless",
         "ERdivERmsy-calc-dimensionless",
         "FdivFmsy-dimensionless",
         "FdivFmsy-calc-dimensionless",
         "ERdivERmgt-dimensionless",
         "ERdivERmgt-calc-dimensionless",
         "FdivFmgt-dimensionless",
         "FdivFmgt-calc-dimensionless",
         "ERdivERmsy-conv-dimensionless",
         "FdivFmsy-conv-dimensionless",
         "ERdivERmsy-est-dimensionless")

bbmgt =c("SSBdivSSBmgt-dimensionless",
         "SSBdivSSBmgt-calc-dimensionless",
         "TBdivTBmgt-dimensionless",
         "TBdivTBmgt-calc-dimensionless",
         "SSBdivSSBmsy-dimensionless",
         "SSBdivSSBmsy-calc-dimensionless",
         "TBdivTBmsy-dimensionless",
         "TBdivTBmsy-calc-dimensionless",
         "TNdivTNmsy-calc-dimensionless",
         "SSBdivSSBmsy-conv-dimensionless",
         "TBdivTBmsy-conv-dimensionless",
         "SSBdivSSBmsy-est-dimensionless",
         "TBdivTBmsy-est-dimensionless")

ffmgt =c("ERdivERmgt-dimensionless",
         "ERdivERmgt-calc-dimensionless",
         "FdivFmgt-dimensionless",
         "FdivFmgt-calc-dimensionless",
         "ERdivERmsy-dimensionless",
         "ERdivERmsy-calc-dimensionless",
         "FdivFmsy-dimensionless",
         "FdivFmsy-calc-dimensionless",
         "ERdivERmsy-conv-dimensionless",
         "FdivFmsy-conv-dimensionless",
         "ERdivERmsy-est-dimensionless")

stock=c("TB-MT",
        "SSB-MT")

yield=c("TC-MT",
        "TL-MT")

f    =c("ER-ratio",
        "ER-calc-ratio")

bmsy =c("TBmsy-MT",
        "TBmsy-pr-MT",
        "TBmsy-extr-MT",
        "TBmsy-calc-MT",
        "SSBmsy-MT (converted)",
        "SSBmsy-pr-MT (converted)",
        "SSBmsy-extr-MT (converted)",
        "SSBmsy-calc-MT (converted)",
        "TB0-MT (converted)",
        "SSB0-MT (converted)",
        "TBmsy-conv-MT",
        "SSBmsy-conv-MT (converted)",
        "TBmsy-est-MT",
        "SSBmsy-est-MT (converted)")

hmsy  =c("ERmsy-ratio",
         "ERmsy-pr-ratio",
         "ERmsy-extr-ratio",
         "ERmsy-calc-ratio",
         "ERmsy-mvo-ratio",
         "ERmsy-conv-ratio",
         "ERmsy-est-ratio")

msy =c("MSY-MT",
       "MSY-calc-MT",
       "MSY-mvo-MT",
       "MSY-conv-MT",
       "MSY-est-MT")

bmgt=c("TBmgt-MT",
       "SSBmgt-MT (converted)")

hmgt=c("ERmgt-ratio")

dat=c("B","Biomass; may be either total biomass or spawning stock biomass",
      "Bmgt","Biomass at management target reference point",
      "Bmsy","Biomass at MSY",
      "Cadv","Scientifically advised catch",
      "CdivMSY","Catch divided by MSY",
      "Cpair","Catch corresponding to TAC and Cadv",
      "CPUE","Catch per unit effort",
      "EFFORT","Measure of fishing effort (depends on fishery)",
      "ER","Exploitation rate (annual proportion)",
      "F","Fishing mortality (instantaneous rate)",
      "MSY","Maximum Sustainable Yield",
      "RecC","Recreational catch",
      "SSB","Spawning stock biomass",
      "survB","Survey biomass",
      "TAC","Total allowable catch",
      "TB","Total biomass",
      "TC","Total catch",
      "TL","Total landings",
      "TN","Total abundance; in numbers",
      "U","Harvest rate; may be either exploitation rate or fishing mortality",
      "Umsy","Harvest rate at MSY",
      "Umgt","Harvest rate at management target reference point")
acronyms=dat[seq(2,length(dat),2)]
names(acronyms)=dat[seq(1,length(dat),2)]
rm(dat)

key=list("acronyms"=acronyms,"bbmgt"=bbmgt,"bbmsy"=bbmsy,"bmgt"=bmgt,"bmsy"=bmsy,"f"=f,"ffmgt"=ffmgt,"ffmsy"=ffmsy,"hmgt"=hmgt,"hmsy"=hmsy,"key"=key,"msy"=msy,"stock"=stock,"yield"=yield) 
  
save(key,assessment,file=file.path(dirRes,"key.RData"))
  
stock  =transform(subset(timeseries,tsid%in%sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%bbmsy]),year=tsyear,bbmsy=tsvalue)[,-(5:6)]
harvest=transform(subset(timeseries,tsid%in%sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%ffmsy]),year=tsyear,ffmsy=tsvalue)[,-(5:6)]
catch  =transform(subset(timeseries,tsid%in%sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%yield]),year=tsyear,catch=tsvalue)[,-(5:6)]

stock$tsid  =factor(stock$tsid,  levels=bbmsy)
harvest$tsid=factor(harvest$tsid,levels=ffmsy)
catch$tsid  =factor(catch$tsid,  levels=yield)
```


## Time Series

Summary of variables in the RAM Legacy database 

#### Spawning stock biomass
```{r}
sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%bbmsy][1:4]
```

#### Total Biomass
```{r}
sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%bbmsy][5:8]
```

#### Fishing mortality (instantaneous rate)
```{r}
sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%ffmsy][5:8]
```

#### Exploitation rate (annual proportion)
```{r}
sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%ffmsy][1:4]
```

#### Total catch
```{r}
sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%yield][1]
```

#### Total landings 
```{r}
sort(unique(timeseries$tsid))[sort(unique(timeseries$tsid))%in%yield][2]
```

```{r, check}
## Filter on availability of time series of $SSB:B_{MSY}$ and $F:F_{MSY}$
sid=subset(timeseries, tsid%in%c("SSBdivSSBmsy-dimensionless","FdivFmsy-dimensionless","TC-MT"))
chk=with(sid,table(assessid,tsid))

pass=names(chk[chk[,1]>0&chk[,2],])

sid=dimnames(chk[chk[,1]>0&chk[,2],])$assessid
ts=subset(timeseries, assessid%in%sid&tsid%in%c("SSBdivSSBmsy-dimensionless","FdivFmsy-dimensionless","SSB-MT","TC-MT","TL-MT"))
ts=cast(ts,assessid+stockid+stocklong+tsyear~tsid)

names(ts)[4:9]=c("year","harvest","ssb","stock","catch","landings")
ts$u=1-exp(-ts$harvest)
ts=transform(ts,catch=ifelse(is.na(catch),landings,catch))

ts=subset(ts,(!is.na(stock)|!is.na(catch)))
save(ts,file=file.path(dirDat,"ts.RData"))
```



```{r}
load(file.path(dirDat,"ts.RData"))
load(file.path(dirDat,"trfmo.RData"))

ts=rbind.fill(cbind("what"="RAM",merge(ts,stockid[,c("stockid","species")])),
              cbind("what"="RFMO",trfmo))[,c("what","assessid","species","year","stock","catch","harvest")]

ts=ddply(ts,.(what,assessid), with, {
  dat=merge(data.frame(year=min(year,na.rm=T):max(year,na.rm=T)),
            data.frame("species"=species,"year"=year,"stock"=stock,"catch"=catch,"harvest"=harvest),by="year",all.x=TRUE)})

ts=subset(ts,(!is.na(catch))|(!is.na(stock))) 
save(ts,file=file.path(dirDat,"ts.RData"))  
```


## Summary plots
```{r, ts-catch}
ggplot(ts)+  
  geom_path(aes(year,catch,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Catch")
```

**Figure `r iFig=iFig+1; iFig`** Timeseries of catch.


```{r, ts-stock}
ggplot(ts)+
  geom_path(aes(year,stock,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab(expression(SSB:B[MSY]))
```

**Figure `r iFig=iFig+1; iFig`** Timeseries of spawning stock biomass.

```{r, ts-harvest}
ggplot(ts)+
  geom_path(aes(year,harvest,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Harvest rate")
```

**Figure `r iFig=iFig+1; iFig`** Timeseries of harvest rate.

```{r, sh}
ggplot(ts)+  
  geom_path(aes(stock,harvest,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+ylab("Harvest Rate")+xlab(expression(SSB:B[MSY]))
```

**Figure `r iFig=iFig+1; iFig`** Trajectories of harvest rate v spawning stock biomass.

```{r, ts-sp, eval=FALSE}
sp=ddply(subset(ts,!is.na(ssb)|is.na(catch)),.(assessid,what), with, {data.frame(year=year[-length(ssb)],
                                           sp  =ssb[-1]-ssb[-length(ssb)]+catch[-length(ssb)],
                                           ssb =ssb[-length(ssb)])})

ggplot(sp)+
  geom_path(aes(year,sp,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Surplus Production")
```


```{r, trj-sp, eval=FALSE}
sp=ddply(subset(ts,!is.na(ssb)),.(assessid,what), with, {data.frame(year=year[-length(ssb)],
                                           sp  =ssb[-1]-ssb[-length(ssb)]+catch[-length(ssb)],
                                           ssb =ssb[-length(ssb)])})

ggplot(sp)+
  geom_path(aes(ssb,sp,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Surplus Production")
```


```{r, msy}
names(stock)[3]="species"
bioparams=subset(bioparams,assessid%in%sid)
msy=subset(bioparams,bioid%in%c("SSBmsy-MT","MSY-MT","SSB0-MT"))
msy=cast(msy,stockid+assessid~bioid,value="biovalue")
names(msy)[3:5]=c("msy","K","bmsy")

msy=mutate(msy, msy=as.numeric(as.character( msy)),
                bmsy=as.numeric(as.character(bmsy)),
                hmsy=msy/bmsy)

msy$K=as.numeric(as.character(msy$K))
msy$shape=msy$bmsy/msy$K
msy=adply(msy, 1, function(x) data.frame(p=optimise(function(x,y) (y-(1/(1+x))^(1/x))^2,c(-0.9999,10),y=x$shape)$minimum))
msy=transform(msy,r=(1+p)*(msy/bmsy))

msy=subset(msy,!is.na(K))
msy=merge(msy[,-7],stockid[,c("stockid","species")])

save(msy,file=file.path(dirRes,"msy.RData"))  
```

```{r, lh}
ts=merge(ts,stockid[,c("stockid","species")])
lh=subset(fb,species%in%c(unique(ts$species),unique(trfmo$species)))

#ref=merge(msy,stockid,by="stockid")
lh[is.na(lh["lmat"]),"lmat"]=(lh[is.na(lh["lmat"]),"lmatmin"]+lh[is.na(lh["lmat"]),"lmatmax"])/2
lh=ddply(lh,.(species), with, data.frame(k   =mean(k,   na.rm=T),
                                         linf=mean(linf,na.rm=T),
                                         t0  =mean(t0,  na.rm=T),
                                         l50 =mean(lmat,na.rm=T),
                                         a50 =mean(amat,na.rm=T),
                                         a   =mean(a,   na.rm=T),
                                         b   =mean(b,   na.rm=T)))

lh$t0=pmin(-0.1,lh$t0)
lh[,-1][is.na(lh[,-1])]=NA

save(lh,file=file.path(dirRes,"lh.RData"))
```

```{r, kb}
kb=rbind(ddply(ts,   .(assessid),with, data.frame(stock=stock[year==max(year)],harvest=harvest[year==max(year)]))[,c("stock","harvest")],
         ddply(trfmo,.(assessid),with, data.frame(stock=stock[year==max(year)],harvest=harvest[year==max(year)]))[,c("stock","harvest")])

kobePhaseMar(kb,xlim=4,ylim=4)
```

**Figure `r iFig=iFig+1; iFig`** Kobe Phase plot for selected RAM Legacy database and tRFMO assessments.

```{r}
library(grid)

FAOPhaseMar(kb[,c("stock","harvest")],xlim=4,ylim=4)
```

**Figure `r iFig=iFig+1; iFig`** FAO plot for selected RAM Legacy database assessments and tRFMO assessments.

```{r}
msyNm=names(bioparams_values_views)[c(3:5,8,9,11,12,20)]
mgtNm=names(bioparams_values_views)[c(6,7,14,15,16,17)]
limNm=names(bioparams_values_views)[c(18,19,21,22,23,24)]
```

```{r, msy2, fig.width=8, fig.height=8}
ggpairs(transmute(msy,r=r,shape=bmsy/K))+theme_bw() 
```

**Figure `r iFig=iFig+1; iFig`** Relationship between population growth rate ($r$) and the ratio of $B_{MSY}:K$ (shape) based on selected data rich assessments.
