---
title: "FAO VoI" 
subtitle: "Figures"
author: "Laurence Kell"
output: rmarkdown:::html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---
Here are the time series for the new "RAM" DB, there are now 85 stocks, some with multiple assessments.

Zig-Zags occur for Shaefer when r is high

There are 6 plots of jabba-fits
  + Jabba with stock/bmsy as an index + final depletion provided as a prior
  + Jabba with stock/bmsy as an index
  + Jabba-COM with known final and initial depletion
  + Jabba-COM with known final and  heuristic for initial depletion
  + Jabba-COM with known initial and  heuristic for final depletion
  + Jabba-COM with heuristic for final & initial depletion 

### JABBA defaults
```{r}
sa=list(assessment  ="com",
        model.type  ="Pella",
        sigma.proc  =TRUE,
        igamma      = c(4,0.01),
        proc.dev.all=TRUE,
        sigma.est   =FALSE,
        fixed.obsE  =0.05)
```
  
```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =TRUE,
               cache.path="cache/figs/",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =6,
               fig.path  ="../tex/figs/",
               dev       ="png")

options(digits=3)

iFig=0
```

```{r, pkgs, echo=FALSE, message=FALSE}
library(reshape)
library(plyr)
library(dplyr)
library(ggplot2)
library(GGally)
library(kobe)

library(FLCore)
library(FLife)
library(popbio)
library(mydas) 

library(grid)
```

```{r, dir, echo=FALSE, message=FALSE}
dirMy ="/home/laurence-kell/Desktop/papers/COM"
dirDat=file.path(dirMy,"data")
dirRes=file.path(dirMy,"results")
dirInp=file.path(dirMy,"inputs") 
```

```{r}
source("/home/laurence-kell/Desktop/flr/kobe/R/trend-plot.R")
source('/home/laurence-kell/Desktop/flr/mpb/R//jabba-com.R') 
```


```{r}
dirDat="/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI/results"
load(file.path(dirDat,"ts.RData")) 
```

```{r,eval=!TRUE}
head(bioparams_values_views)
```

## Summary of Data

```{r, ts-ssb, fig.height=4, fig.width=8}
library(grid)

trks=transmute(subset(ts,!is.na(stock)&year%in%1950:2012),year=year,series=stock,run=assessid)
pts =ddply(trks,.(run), function(x) subset(trks,year==max(year))) 
t1=trendPhaseMar(trks,pts,ylim=5,layer=geom_text(aes(x=1952,y=4.5,label="C")))
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for the RAM Legacy database.

```{r, ts-f, fig.height=4, fig.width=8}
library(grid) 

trks=transmute(subset(ts,!is.na(stock)&year%in%1950:2012),year=year,series=harvest,run=assessid)
pts =ddply(trks,.(run), function(x) subset(trks,year==max(year)))
t2=trendPhaseMar(trks,pts,ylim=5,ylab=expression(F:F[MSY]),layer=geom_text(aes(x=1952,y=4.5,label="B")))
```

**Figure `r iFig=iFig+1; iFig`** Time series of  $F:F_{MSY}$ for the RAM Legacy database.


```{r, ts-c, fig.height=4, fig.width=8}
library(grid)  
load("/home/laurence-kell/Desktop/papers/COM2/data/msyts.RData")

trks=transmute(subset(msy,year%in%1950:2012),run=scenario,year=year,series=series)
pts =ddply(trks,.(run), function(x) subset(trks,year==max(year)))
t3=trendPhaseMar(trks,pts,ylab=expression(Yield:MSY),ylim=5,layer=geom_text(aes(x=1952,y=4.5,label="A")))
```

**Figure `r iFig=iFig+1; iFig`** Time series of $Catch:MSY$ for the RAM Legacy database.


```{r, kobe, fig.height=6, fig.width=6}
kobe:::kobePhaseMar3(ddply(subset(ts,!is.na(stock)),.(assessid), with, {data.frame(
  stock  =stock[length(stock)],
  harvest=harvest[length(stock)])}),ylim=4,xlim=4)
```

**Figure `r iFig=iFig+1; iFig`** Kobe phase plot.

```{r, stocks-1, fig.width=10,fig.height=3}
load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData")

com=subset(com,bmsyk!=0.2) 

com=ddply(com,.(scenario,bmsyk), transform, productivity=ifelse(max(r)==r,"high","Low"))
load(file.path(dirDat,"ts.RData"))

nms=names(table(com$scenario))
ggplot(data.frame(assessid=nms,scenario=substr(nms,1,12)))+
  facet_wrap(~assessid,scale="free",ncol=10)+
  geom_label(aes(1,1,label=scenario),size=2.5)+
  theme_bw(0)
```

### Fits to perfect index

```{r, stocks-2, fig.width=10,fig.height=8}
ggplot(subset(com,perfect&depletion))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+
  theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba fit to perfect index and final depletion.


```{r, stocks-3, fig.width=10,fig.height=8}
ggplot(subset(com,perfect&!depletion))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+
  theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba fit to perfect index alone.


### Fits to catch only
```{r, stocks-4, fig.width=10,fig.height=8}
ggplot(subset(com,!perfect&initial=="Actual"&final=="Actual"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with actual initial and final depletion.


```{r, stocks-5, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Heuristic"&final=="Actual"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with heuistic for initial and actual final depletion.

```{r, stocks-6, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Actual"&final=="Heuristic"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with actual initial and heuristic for final depletion.


```{r, stocks-7, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Heuristic"&final=="Heuristic"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green"[-3])) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with heuristics for initial and final depletion.


```{r, cf, fig.width=6,fig.height=6.5}
load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData")

com=subset(com,bmsyk!=0.2)
com=transform(com,initial=factor(initial,labels=c("Initial Known","Heuristic")),
                   final  =factor(final, labels=c("Final Known","Heuristic")))

dat=ddply(subset(com,!is.na(om)&!is.na(stock)&!perfect),.(scenario), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))
dat=ddply(dat,.(scenario), transform, r=(r==max(r)))

s4=ggplot(dat)+
  facet_grid(initial~final)+
  #geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0.1,0.1,3.9,3.9),y=c(3.9,0.5,0.5,3.9),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk),shape=r))+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=1.0),col="red")+
  geom_vline(aes(xintercept=1.0),col="red")+
    geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw(10)+theme(legend.position="none")+
  xlab("Data Rich")+ylab("Estimate")+
  scale_shape_manual(values=c(21,22),label=c("Low","High"))
s4 
```

**Figure `r iFig=iFig+1; iFig`** Plots of estimates verses RAM values of $B/B_{MSY}$.



```{r, cf2, fig.width=6,fig.height=6.5}
load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData")

com=subset(com,bmsyk!=0.2)
com=transform(com,initial=factor(initial,labels=c("Initial Known","Heuristic")),
                   final  =factor(final, labels=c("Final Known","Heuristic")))

dat=ddply(subset(com,!is.na(om)&!is.na(stock)&!perfect),.(scenario), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))
dat=ddply(dat,.(scenario), transform, r=(r==max(r)))

s4=ggplot(dat)+
  facet_grid(initial~final)+
  #geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0.1,0.1,3.9,3.9),y=c(3.9,0.5,0.5,3.9),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk),shape=r))+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=1.0),col="red")+
  geom_vline(aes(xintercept=1.0),col="red")+
    geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw(10)+theme(legend.position="none")+
  xlab("Data Rich")+ylab("Estimate")+
  scale_shape_manual(values=c(21,22),label=c("Low","High"))
s4 
```

**Figure `r iFig=iFig+1; iFig`** Plots of estimates verses RAM values of $B/B_{MSY}$.


```{r, cf-jabba, fig.width=6,fig.height=6.5}
load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData")

com=subset(com,bmsyk!=0.2)

dat=ddply(subset(com,!is.na(om)&!is.na(stock)&perfect&!depletion),.(scenario), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r), transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))
dat=ddply(dat,.(scenario), transform, r=(r==max(r)))

ggplot(dat)+ 
  geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0,0,4,4),y=c(4,0.5,0.5,4),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk),shape=r))+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=1.0),col="red")+
  geom_vline(aes(xintercept=1.0),col="red")+
  geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw(10)+theme(legend.position="bottom")+
  xlab("Data Rich")+ylab("Estimate")+
  scale_shape_manual(values=c(21,22),label=c("Low","High"))
```

**Figure `r iFig=iFig+1; iFig`** JABBA plots of estimates verses RAM values of $B/B_{MSY}$.

```{r, fig-4, fig.width=6,fig.height=6.5}
load("/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI/results/withIndx.RData")

dat=subset(withIndx,!is.na(index))
dat=ddply(dat,.(scenario,bmsyk,r), subset, year>=max(year))
dat=ddply(dat,.(scenario,bmsyk,r), transmute, data.frame(year==max(year),om=mean(index),mp=mean(stock)))
dat=ddply(dat,.(scenario), transform, r=(r==max(r)))

s1=ggplot(dat)+
  geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0,0,4,4),y=c(4,0.5,0.5,4),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk),shape=r))+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE,span=1)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=1.0),col="red")+
  geom_vline(aes(xintercept=1.0),col="red")+
  geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw(10)+theme(legend.position="bottom")+
  xlab("Data Rich")+ylab("Estimate")+
  scale_shape_manual(values=c(21,22),label=c("Low","High"))
s1 
```

**Figure `r iFig=iFig+1; iFig`** JABBA plots of estimates verses RAM values of $B/B_{MSY}$. xxx

```{r}
load(file.path(dirDat,"ts.RData"))

heuristic=ddply(subset(ts,!is.na(catch)&!is.na(stock)),.(assessid), with, 
                data.frame("Heuristic"=dFinalPrior(catch),
                           "Actual"   =stock[year==max(year)]))
heuristic=with(heuristic,mydas:::roc(Actual>1,Heuristic))
```

```{r, roc, fig.width=7, fig.height=6.5}
load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData") #file.path(dirRes,"com.RData"))
com=subset(com,bmsyk!=0.2)
com=transform(com,initial=factor(initial,labels=c("Initial Known","Heuristic")),
                   final  =factor(final,  labels=c("Final Known","Heuristic"))) 
  
dat=subset(com,!is.na(om)&!is.na(stock)&!perfect)
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final),transmute, 
          data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(bmsyk,r,initial,final),with, mydas:::roc(om>1,mp))
ref=ddply(roc,.(bmsyk,r,initial,final), transform, ss=FPR^2+(1-TPR)^2)
ref=ddply(ref,.(bmsyk,r,initial,final), subset, ss==min(ss))

ref1=ddply(roc, .(bmsyk,r,initial,final), subset, abs(reference-1)==min(abs(reference-1)))

b4=ggplot(roc)+
  geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  facet_grid(initial~final)+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  #geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  #scale_shape_manual(   "Reference",          values=c(22,21)[2],       labels=c("Best","BMSY")[2])+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="none") 
b4

save(roc,file="/home/laurence-kell/Desktop/tmp/roc1.RData")
```

```{r}
library(DescTools)

load("/home/laurence-kell/Desktop/tmp/roc1.RData")

roc$r=c("Low","High")[as.numeric(roc$r)+1]
cast(ddply(roc,.(final,initial,bmsyk,r), with, round(AUC(FPR,TPR),2)),final+initial~bmsyk+r,value="V1")
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA-COM, columns are Initial and rows Final depeletion derivation.

```{r}
save(roc,heuristic,ref,ref1,file="/home/laurence-kell/Desktop/tmp/roc.RData") 
```


```{r, roc-jabba, fig.width=6, fig.height=6.5}
load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData") #file.path(dirRes,"com.RData"))
com=subset(com,bmsyk!=0.2)

dat=subset(com,perfect&depletion)
dat=ddply(subset(dat,!is.na(om)&!is.na(stock)),.(scenario,perfect,depletion,bmsyk,r,initial,final), subset, year==max(year))
dat=ddply(dat,.(scenario,perfect,depletion,bmsyk,r,initial,final),transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(perfect,depletion,bmsyk,r,initial,final),with, mydas:::roc(om>1,mp))
#roc$r=c("High","Low")[roc$r]

ref=ddply(roc,.(bmsyk,r), transform, ss=FPR^2+(1-TPR)^2)
ref=ddply(ref,.(bmsyk,r), subset, ss==min(ss))

ref1=ddply(subset(roc,perfect&depletion), .(bmsyk,r), subset, abs(reference-1)==min(abs(reference-1)))

b1=ggplot(subset(roc,perfect&depletion))+
  geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  #geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4,,shape=21)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  #scale_shape_manual(   "Reference",          values=c(22,21)[2],       labels=c("Best","BMSY")[2])+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="bottom")
b1
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA


```{r}
library(DescTools)
with(heuristic, AUC(FPR,TPR))
```

```{r, fig-5, fig.width=6, fig.height=6.5}
load("/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI/results/withIndx.RData")
names(withIndx)[c(3,6)]=c("mp","om")

dat=ddply(subset(withIndx,!is.na(om)&!is.na(mp)),.(scenario,bmsyk,r), subset, year==max(year))

dat=ddply(dat,.(scenario,bmsyk,r),subset, year>=max(year))
dat=ddply(dat,.(scenario,bmsyk,r),transmute, data.frame(year=max(year),om=mean(om),mp=mean(mp)))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(bmsyk,r),with, mydas:::roc(om>1,mp))

ref=ddply(roc,.(bmsyk,r), transform, ss=FPR^2+(1-TPR)^2)
ref=ddply(ref,.(bmsyk,r), subset, ss==min(ss))

ref1=ddply(roc, .(bmsyk,r), subset, abs(reference-1)==min(abs(reference-1)))

ggplot(roc)+
  geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  #geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4,shape=21)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  #scale_shape_manual(   "Reference",          values=c(22,21)[2],       labels=c("Best","BMSY")[2])+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="bottom")

save(roc,file="/home/laurence-kell/Desktop/tmp/roc2.RData")
```

```{r}
library(DescTools)

load("/home/laurence-kell/Desktop/tmp/roc2.RData")

head(roc)
roc$r=c("Low","High")[as.numeric(roc$r)+1]
cast(ddply(roc,.(bmsyk,r), with, round(AUC(FPR,TPR),2)),bmsyk~r)
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA

## Fishing Mortality

### Fits to perfect index

```{r, harvest-2, fig.width=10,fig.height=8}
dirDat="/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI/results"
load(file.path(dirDat,"ts.RData"))
load("/home/laurence-kell/Desktop/papers/COM2/data/trfmo.RData")

load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData")

com=subset(com,bmsyk!=0.2)

com=merge(com,rbind(transmute(ts,   scenario=assessid,year=year,om.f=harvest),
                    transmute(trfmo,scenario=assessid,year=year,om.f=harvest))
                    ,x.all=TRUE)
com=ddply(com,.(scenario,bmsyk), transform, productivity=ifelse(max(r)==r,"high","Low"))
nms=names(table(com$scenario))

ggplot(subset(com,perfect&depletion))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,harvest,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om.f))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+
  theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $F:F_{MSY}$ for Jabba fit to perfect index and final depletion.


```{r, harvest-3, fig.width=10,fig.height=8}
ggplot(subset(com,perfect&!depletion))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,harvest,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om.f))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+
  theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $F:F_{MSY}$ for Jabba fit to perfect index alone.


### Fits to catch only
```{r, harvest-4, fig.width=10,fig.height=8}
ggplot(subset(com,!perfect&initial=="Actual"&final=="Actual"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,harvest,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om.f))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 

```

**Figure `r iFig=iFig+1; iFig`** Time series of $F:F_{MSY}$ for Jabba-COM fit with actual initial and final depletion.


```{r, harvest-5, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Heuristic"&final=="Actual"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,harvest,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om.f))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $F:F_{MSY}$ for Jabba-COM fit with heuistic for initial and actual final depletion.

```{r, harvest-6, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Actual"&final=="Heuristic"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,harvest,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om.f))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $F:F_{MSY}$ for Jabba-COM fit with actual initial and heuristic for final depletion.


```{r, harvest-7, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Heuristic"&final=="Heuristic"))+
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,harvest,col=as.character(bmsyk),linetype=productivity))+
  geom_line(aes(year,om.f))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green"[-3])) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $F:F_{MSY}$ for Jabba-COM fit with heuristics for initial and final depletion.


```{r, cf-harvest, fig.width=6,fig.height=6.5}
com=subset(com,bmsyk!=0.2)
com=transform(com,initial=factor(initial,labels=c("Initial Known","Heuristic")),
                   final  =factor(final,  labels=c("Final Known","Heuristic")))

dat=ddply(subset(com,!is.na(om)&!is.na(stock)&!perfect),.(scenario), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), transmute, data.frame(year=max(year),om=om.f[year==max(year)],mp=harvest[year==max(year)]))

ggplot(dat)+
  facet_grid(initial~final)+
  geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0,0,4,4),y=c(4,0.5,0.5,4),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk)),shape=21)+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=1.0),col="red")+
  geom_vline(aes(xintercept=1.0),col="red")+
    geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw()+theme(legend.position="bottom")+
  xlab("Data Rich")+ylab("Estimate")
```

**Figure `r iFig=iFig+1; iFig`** Plots of estimates verses RAM values of $F/F_{MSY}$.


```{r, cf-jabba-harvest, fig.width=6,fig.height=6.5}
ggplot(dat)+
  geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0,0,4,4),y=c(4,0.5,0.5,4),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk)),shape=21)+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=1.0),col="red")+
  geom_vline(aes(xintercept=1.0),col="red")+
  geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw(10)+theme(legend.position="bottom")+
  xlab("Data Rich")+ylab("Estimate")
```

**Figure `r iFig=iFig+1; iFig`** JABBA plots of estimates verses RAM values of $F/F_{MSY}$.


```{r}
load(file.path(dirDat,"ts.RData"))

heuristic=ddply(subset(ts,!is.na(catch)&!is.na(stock)),.(assessid), with, 
                data.frame("Heuristic"=dFinalPrior(catch),
                           "Actual"   =stock[year==max(year)]))
heuristic=with(heuristic,mydas:::roc(Actual>1,Heuristic))
```

```{r, roc-harvest, fig.width=7, fig.height=6.5}
com=transform(com,initial=factor(initial,labels=c("Initial Known","Heuristic")),
                   final =factor(final,  labels=c("Final Known","Heuristic")))

  
dat=subset(com,!is.na(om)&!is.na(harvest)&!perfect)
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final),transmute, 
          data.frame(year=max(year),om=om[year==max(year)],mp=harvest[year==max(year)]))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(bmsyk,r,initial,final),with, mydas:::roc(om>1,mp))
ref=ddply(roc,.(bmsyk,r,initial,final), transform, ss=FPR^2+(1-TPR)^2)
ref=ddply(ref,.(bmsyk,r,initial,final), subset, ss==min(ss))

ref1=ddply(roc, .(bmsyk,r,initial,final), subset, abs(reference-1)==min(abs(reference-1)))

f4=ggplot(roc)+
  #geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  facet_grid(initial~final)+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  #geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4,shape=21)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  #scale_shape_manual(   "Reference",          values=c(22,21)[2],    labels=c("Best","BMSY"))+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="none") 
f4
```


```{r}
library(DescTools)

roc$r=c("Low","High")[as.numeric(roc$r)+1]
cast(ddply(roc,.(final,initial,bmsyk,r), with, round(AUC(FPR,TPR),2)),final+initial~bmsyk+r,value="V1")
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA-COM, columns are Initial and rows Final depeletion derivation.


```{r, roc-jabba-harvest, fig.width=6, fig.height=6.5}
dat=subset(com,perfect&depletion)
dat=ddply(subset(dat,!is.na(om)&!is.na(harvest)),.(scenario,perfect,depletion,bmsyk,r,initial,final), subset, year==max(year))
dat=ddply(dat,.(scenario,perfect,depletion,bmsyk,r,initial,final),transmute, data.frame(year=max(year),om=om[year==max(year)],mp=harvest[year==max(year)]))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(perfect,depletion,bmsyk,r,initial,final),with, mydas:::roc(om>1,mp))
#roc$r=c("High","Low")[roc$r]

ref=ddply(roc,.(bmsyk,r), transform, ss=FPR^2+(1-TPR)^2)
ref=ddply(ref,.(bmsyk,r), subset, ss==min(ss))

ref1=ddply(subset(roc,perfect&depletion), .(bmsyk,r), subset, abs(reference-1)==min(abs(reference-1)))

ggplot(subset(roc,perfect&depletion))+
  #geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  #geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4,shape=21)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  #scale_shape_manual(   "Reference",          values=c(22,21)[2],       labels=c("Best","BMSY"))+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA


```{r, roc-jabba-harvest-index0.5, fig.width=6, fig.height=6.5}
load("/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI/results/withIndx.RData")
load("/home/laurence-kell/Desktop/papers/COM2/results/com.RData")
dirDat="/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI/results"
load(file.path(dirDat,"ts.RData"))
names(ts)[2]="scenario" 

dat=merge(withIndx,ts[,c("scenario","year","harvest")],by=c("scenario","year"))
names(dat)[c(4,9)]=c("mp","om")

dat=ddply(subset(dat,!is.na(om)&!is.na(mp)),.(scenario,bmsyk,r), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r),transmute, data.frame(year=max(year),om=om[year==max(year)],mp=mp[year==max(year)]))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(bmsyk,r),with, mydas:::roc(om>1,mp))
#roc$r=c("High","Low")[roc$r]

ref1=ddply(roc, .(bmsyk,r), subset, abs(reference-1)==min(abs(reference-1)))

f1=ggplot(subset(roc))+
  #geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  #geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4,shape=21)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  #scale_shape_manual(   "Reference",          values=c(22,21)[2],       labels=c("Best","BMSY"))+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="bottom")
f1
```


```{r}
library(DescTools)

roc$r=c("Low","High")[as.numeric(roc$r)+1]
cast(ddply(roc,.(bmsyk,r), with, round(AUC(FPR,TPR),2)),bmsyk~r,value="V1")
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA with half index


```{r, retro, fig.width=6, fig.height=6.5}
load("/home/laurence-kell/Desktop/papers/COM2/results/retro.RData")

dat=merge(transform(subset(retro,tail==year),y=stock)[    ,c("scenario", "bmsyk","r","perfect","year","run","y")],
            transform(subset(retro,tail==max(year)),x=stock)[,c("scenario", "bmsyk","r","perfect","year","run","x")])
  
ret=ddply(dat,.(scenario,bmsyk,r,perfect,run),with, mean((y-x)/x))

ggplot(transform(subset(ret,run%in%c(1,2,4)),run=factor(run,labels=c("With Index","COM with Depletion Known","COM with Heuristic"))))+
  geom_histogram(aes(V1))+facet_grid(run~.)+theme_bw()+
  xlab("Mohn's rho")+ylab("")
```


```{r}
load("/home/laurence-kell/Desktop/papers/COM2/results/retro.RData")

com=subset(com,bmsyk!=0.2)
com=transform(com,initial=factor(initial,labels=c("Initial Known","Heuristic")),
                   final  =factor(final, labels=c("Final Known",  "Heuristic")))
com=ddply(com,.(scenario,bmsyk), transform, r=ifelse(r==max(r),"high","low"))

dat=ddply(subset(com,!is.na(om)&!is.na(stock)&!perfect),.(scenario), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))

tm=ddply(dat,.(initial,final,bmsyk,r), with, cor(om,mp))
cast(tm,initial+final~bmsyk+r,value="V1",mean)

tm=ddply(dat,.(initial,final,bmsyk,r), with, cor(order(om),order(mp)))
cast(tm,initial+final~bmsyk+r,value="V1",mean)
```

`r round(runif(1,1,350)) `



```{r, fig.height=4,fig.width=8}
library(ggpubr)
ggarrange(s1,
          ggarrange(s4, labels = c("B")), 
          nrow = 1,ncol=2,
          labels = "A",
          common.legend = TRUE) 
```


```{r, fig.height=4,fig.width=8}
library(ggpubr) 
ggarrange(b1,     
          ggarrange(b4, labels = c("B")), 
          nrow = 1,ncol=2,
          labels = "A",
          common.legend = TRUE) 
```


```{r, fig.height=4,fig.width=8}
library(ggpubr) 
ggarrange(f1,                      
          ggarrange(f4, labels = c("B")), 
          nrow = 1,ncol=2,
          labels = "A" ,
          common.legend = TRUE) 
```


```{r, ts, fig.width=6, fig.height=10}
library(grid)  
library(gridExtra)

vplayout<-function(x, y)
      viewport(layout.pos.row = x, layout.pos.col = y)
    
grid.newpage()

pushViewport(viewport(layout = grid.layout(15, 6)))
print(t3[[2]]+coord_flip(xlim=c(0,5)), vp=vplayout( 2: 5,6))    
print(t2[[2]]+coord_flip(xlim=c(0,5)), vp=vplayout( 7:10,6))    
print(t1[[2]]+coord_flip(xlim=c(0,5)), vp=vplayout(12:15,6))    

print(t3[[1]], vp=vplayout(2:5,   1:5))             
print(t2[[1]], vp=vplayout(2:5+5,1:5))                     
print(t1[[1]], vp=vplayout(2:5+10, 1:5))                     
```

