---
title: "FAO VoI" 
subtitle: "Figures"
author: "Laurence Kell"
output: rmarkdown:::html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---
Here are the time series for the new "RAM" DB, there are now 85 stocks, some with multiple assessments.

Zig-Zags occur for Shaefer when r is high

There are 6 plots of jabba-fits
  + Jabba with stock/bmsy as an index + final depletion provided as a prior
  + Jabba with stock/bmsy as an index
  + Jabba-COM with known final and initial depletion
  + Jabba-COM with known final and  heuristic for initial depletion
  + Jabba-COM with known initial and  heuristic for final depletion
  + Jabba-COM with heuristic for final & initial depletion 

### JABBA defaults
```{r}
sa=list(assessment  ="com",
        model.type  ="Pella",
        sigma.proc  =TRUE,
        igamma      = c(4,0.01),
        proc.dev.all=TRUE,
        sigma.est   =FALSE,
        fixed.obsE  =0.05)
```
  
```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =TRUE,
               cache.path="cache/figs/",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =6,
               fig.path  ="../tex/figs/",
               dev       ="png")

options(digits=3)

iFig=0
```

```{r, pkgs, echo=FALSE, message=FALSE}
library(reshape)
library(plyr)
library(dplyr)
library(ggplot2)
library(GGally)
library(kobe)

library(FLCore)
library(FLife)
library(popbio)
library(mydas) 

library(grid)
```

```{r, dir, echo=FALSE, message=FALSE}
dirMy ="/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI"
dirDat=file.path(dirMy,"data")
dirRes=file.path(dirMy,"results")
dirInp=file.path(dirMy,"inputs") 
```

```{r}
source("/home/laurence-kell/Desktop/flr/kobe/R/trend-plot.R")
source('/home/laurence-kell/Desktop/flr/mpb/R//jabba-com.R')
```


```{r}
load(file.path(dirDat,"ts.RData")) 
```

```{r,eval=!TRUE}
head(bioparams_values_views)
```

## Summary of Data

```{r, ts-ssb, fig.height=4, fig.width=8}
library(grid)

trks=transmute(subset(ts,!is.na(stock)&year%in%1950:2012),year=year,series=stock,run=assessid)
pts =ddply(trks,.(run), function(x) subset(trks,year==max(year)))

trendPhaseMar(trks,pts,ylim=5)
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for the RAM Legacy database.

```{r, ts-f, fig.height=4, fig.width=8}
library(grid)

trks=transmute(subset(ts,!is.na(stock)&year%in%1950:2012),year=year,series=harvest,run=assessid)
pts =ddply(trks,.(run), function(x) subset(trks,year==max(year)))

trendPhaseMar(trks,pts,ylim=5)
```

**Figure `r iFig=iFig+1; iFig`** Time series of  $F:F_{MSY}$ for the RAM Legacy database.


```{r, ts-c, fig.height=4, fig.width=8}
library(grid)
load(file.path(dirDat,"msy.RData"))

trks=transmute(subset(msy,year%in%1950:2012),run=scenario,year=year,series=series)
pts =ddply(trks,.(run), function(x) subset(trks,year==max(year)))

trendPhaseMar(trks,pts,ylab=expression(F/F[MSY]),ylim=3) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $Catch:MSY$ for the RAM Legacy database.



```{r, kobe, fig.height=6, fig.width=6}
kobe:::kobePhaseMar3(ddply(subset(ts,!is.na(stock)),.(assessid), with, {data.frame(
  stock  =stock[length(stock)],
  harvest=harvest[length(stock)])}),ylim=4,xlim=4)
```

**Figure `r iFig=iFig+1; iFig`** Kobe phase plot.

```{r, stocks-1, fig.width=10,fig.height=3}
load(file.path(dirRes,"com.RData")) 
com=subset(com,bmsyk!=0.2) 

com=ddply(com,.(scenario,bmsyk), transform, productivity=ifelse(max(r)==r,"high","Low"))
load(file.path(dirDat,"ts.RData"))

nms=names(table(com$scenario))
ggplot(data.frame(assessid=nms,scenario=substr(nms,1,12)))+
  facet_wrap(~assessid,scale="free",ncol=10)+  
  geom_label(aes(1,1,label=scenario),size=2.5)+
  theme_bw(0)
```

### Fits to perfect index

```{r, stocks-2, fig.width=10,fig.height=8}
ggplot(subset(com,perfect&depletion))+   
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+ 
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+
  theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba fit to perfect index and final depletion.


```{r, stocks-3, fig.width=10,fig.height=8}
ggplot(subset(com,perfect&!depletion))+   
  facet_wrap(~scenario,scale="free",ncol=10)+
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+ 
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+
  theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba fit to perfect index alone.


### Fits to catch only
```{r, stocks-4, fig.width=10,fig.height=8}
ggplot(subset(com,!perfect&initial=="Actual"&final=="Actual"))+   
  facet_wrap(~scenario,scale="free",ncol=10)+ 
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+ 
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+   
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 

```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with actual initial and final depletion.


```{r, stocks-5, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Heuristic"&final=="Actual"))+   
  facet_wrap(~scenario,scale="free",ncol=10)+ 
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+  
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with heuistic for initial and actual final depletion.

```{r, stocks-6, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Actual"&final=="Heuristic"))+    
  facet_wrap(~scenario,scale="free",ncol=10)+ 
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+ 
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+   
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green")[-3]) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with actual initial and heuristic for final depletion.


```{r, stocks-7, fig.width=10,fig.height=6}
ggplot(subset(com,!perfect&initial=="Heuristic"&final=="Heuristic"))+    
  facet_wrap(~scenario,scale="free",ncol=10)+ 
  geom_line(aes(year,stock,col=as.character(bmsyk),linetype=productivity))+ 
  geom_line(aes(year,om))+
  geom_hline(aes(yintercept=y),col="yellow",data=data.frame(y=1.2,scenario=nms))+
  geom_hline(aes(yintercept=y),col="orange",data=data.frame(y=1.0,scenario=nms))+
  geom_hline(aes(yintercept=y),col="red",   data=data.frame(y=0.8,scenario=nms))+
  theme_bw(0)+theme(legend.position="bottom")+
  scale_color_manual("Ratio between BMSY and K",values=c("red","blue","green"[-3])) 
```

**Figure `r iFig=iFig+1; iFig`** Time series of $B:B_{MSY}$ for Jabba-COM fit with heuristics for initial and final depletion.


```{r, cf, fig.width=6,fig.height=6.5}
load(file.path(dirRes,"com.RData"))
com=subset(com,bmsyk!=0.2)

dat=ddply(subset(com,!is.na(om)&!is.na(stock)&!perfect),.(scenario), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))

ggplot(dat)+
  facet_grid(initial~final)+
  geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0,0,4,4),y=c(4,0.5,0.5,4),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk)),shape=21)+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=0.8),col="red")+
  geom_hline(aes(yintercept=1.0),col="orange")+
  geom_hline(aes(yintercept=1.2),col="yellow")+
  geom_vline(aes(xintercept=0.8),col="red")+
  geom_vline(aes(xintercept=1.0),col="orange")+
  geom_vline(aes(xintercept=1.2),col="yellow")+
  geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw()+theme(legend.position="bottom")+
  xlab("Data Rich")+ylab("Estimate")
```

**Figure `r iFig=iFig+1; iFig`** Plots of estimates verses RAM values of $B/B_{MSY}$.


```{r, cf-jabba, fig.width=6,fig.height=6.5}
load(file.path(dirRes,"com.RData"))
com=subset(com,bmsyk!=0.2)

dat=ddply(subset(com,!is.na(om)&!is.na(stock)&perfect&!depletion),.(scenario), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r), transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))

ggplot(dat)+
  geom_text(aes(x=x,y=y,label=label),data=data.frame(x=c(0,0,4,4),y=c(4,0.5,0.5,4),label=c("FP","TN","FN","TP")))+
  geom_point(aes(om,mp,fill=as.character(bmsyk)),shape=21)+
  geom_smooth(aes(om,mp,col=as.character(bmsyk)),method="loess",se=FALSE)+
  scale_colour_manual("Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_fill_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  geom_hline(aes(yintercept=0.8),col="red")+
  geom_hline(aes(yintercept=1.0),col="orange")+
  geom_hline(aes(yintercept=1.2),col="yellow")+
  geom_vline(aes(xintercept=0.8),col="red")+
  geom_vline(aes(xintercept=1.0),col="orange")+
  geom_vline(aes(xintercept=1.2),col="yellow")+
  geom_line(aes(x,y),data.frame(x=seq(0,3.75,0.01),y=seq(0,3.75,0.01)),linetype=2)+
  theme_bw()+theme(legend.position="bottom")+
  xlab("Data Rich")+ylab("Estimate")
```

**Figure `r iFig=iFig+1; iFig`** JABBA plots of estimates verses RAM values of $B/B_{MSY}$.


```{r}
load(file.path(dirDat,"ts.RData"))

heuristic=ddply(subset(ts,!is.na(catch)&!is.na(stock)),.(assessid), with, 
                data.frame("Heuristic"=dFinalPrior(catch),
                           "Actual"   =stock[year==max(year)]))
heuristic=with(heuristic,mydas:::roc(Actual>1,Heuristic))
```

```{r, roc, fig.width=7, fig.height=6.5}
load(file.path(dirRes,"com.RData"))
com=subset(com,bmsyk!=0.2)

dat=subset(com,!is.na(om)&!is.na(stock)&!perfect)
dat=ddply(dat,.(scenario,bmsyk,r,initial,final), subset, year==max(year))
dat=ddply(dat,.(scenario,bmsyk,r,initial,final),transmute, 
          data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(bmsyk,r,initial,final),with, mydas:::roc(om>1,mp))
ref=ddply(roc,.(bmsyk,r,initial,final), transform, ss=FPR^2+(1-TPR)^2)
ref=ddply(ref,.(bmsyk,r,initial,final), subset, ss==min(ss))

ref1=ddply(roc, .(bmsyk,r,initial,final), subset, abs(reference-1)==min(abs(reference-1)))

ggplot(roc)+
  geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  facet_grid(final~initial)+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,shape="21",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  scale_shape_manual(   "Reference",          values=c(22,21),       labels=c("Best","BMSY"))+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA-COM, columns are Initial and rows Final depeletion derivation.



```{r, roc-jabba, fig.width=6, fig.height=6.5}
load(file.path(dirRes,"com.RData"))
com=subset(com,bmsyk!=0.2)

dat=subset(com,perfect&depletion)
dat=ddply(subset(dat,!is.na(om)&!is.na(stock)),.(scenario,perfect,depletion,bmsyk,r,initial,final), subset, year==max(year))
dat=ddply(dat,.(scenario,perfect,depletion,bmsyk,r,initial,final),transmute, data.frame(year=max(year),om=om[year==max(year)],mp=stock[year==max(year)]))
dat=ddply(dat,.(scenario,bmsyk),transform,r=r>min(r))
roc=ddply(dat,.(perfect,depletion,bmsyk,r,initial,final),with, mydas:::roc(om>1,mp))
#roc$r=c("High","Low")[roc$r]

ref=ddply(roc,.(bmsyk,r), transform, ss=FPR^2+(1-TPR)^2)
ref=ddply(ref,.(bmsyk,r), subset, ss==min(ss))

ref1=ddply(subset(roc,perfect&depletion), .(bmsyk,r), subset, abs(reference-1)==min(abs(reference-1)))

ggplot(subset(roc,perfect&depletion))+
  geom_line(aes(FPR,TPR),data=heuristic,col="purple")+
  geom_path(aes( FPR,TPR,col=as.character(bmsyk),linetype=r))+
  geom_point(aes(FPR,TPR,shape= "1",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref, size=4)+
  geom_point(aes(FPR,TPR,shape="21",fill=as.character(bmsyk),col=as.character(bmsyk),linetype=r),data=ref1,size=4)+
  geom_line(aes(x,y),data.frame(x=seq(0,1,0.01),y=seq(0,1,0.01)))+
  scale_shape_manual(   "Reference",          values=c(22,21),       labels=c("Best","BMSY"))+
  scale_linetype_manual("r Prior",            values=c(1,2),         labels=c("High","Low"))+
  scale_fill_manual(    "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  scale_colour_manual(  "Production Function",values=c("green","red","blue")[-1],labels=c("Pella","Fox","Schaefer")[-1])+
  theme_bw()+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** ROC curves for JABBA

