---
title: "FAO VoI" 
subtitle: "Get tuna RFMO datasets"
author: "Laurence Kell"
output: rmarkdown:::html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---
  
```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =TRUE,
               cache.path="cache/data/trfmo",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =10,
               fig.path  ="../tex/figs/trfmo-",
               dev       ="png")

options(digits=3)

iFig=0
```

```{r, pkgs, echo=FALSE, message=FALSE}
library(reshape)
library(plyr)
library(dplyr)
library(ggplot2)
library(kobe)

library(FLCore)
library(FLife)

library(diags)
library(r4ss)
```

```{r, data, echo=FALSE, message=FALSE}
dirMy ="/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI"
dirInp=file.path(dirMy,"inputs") 
dirDat=file.path(dirMy,"data")
dirRes=file.path(dirMy,"results")
```


```{r, data, echo=FALSE, message=FALSE}
source('~/Desktop/flr/diags/R/ss-prd.R')
```

```{r}
/home/laurence-kell/Desktop/projects/fao/VoI/Report/FAO-VoI/inputs

```


```{r, tRFMO}

setRAM<-function(x){
  rf =getRf(x)
  sp =spFunc(x)[-1,]
  res=transform(sp,stock=ssb/rf[1,"ssbmsy"])
  res=cbind(res,"harvest"=x$Kobe[seq(dim(res)[1]),3])
  res}

dir   =system2("ls",args=dirAss,stdout=TRUE)
dir=dir[dir.exists(file.path(dirAss,dir))]
dir=dir[file.exists(file.path(dirAss,dir,"lkout.rdata"))]

jb=mdply(dir,function(x) {
     load(file.path(dirAss,x,"lkout.rdata"))
     cbind(assessid=x,lkout)})[,-1]

jb$assessid=jb$stockid

ss=data.frame(
file=c(file.path(c("/home/laurence-kell/Dropbox/xval/io-bet",
                   "/home/laurence-kell/Dropbox/xval/io-yft",
                   "/home/laurence-kell/Dropbox/xval/epo-bet",
                   "/home/laurence-kell/Dropbox/xval/epo-yft",
                   "/home/laurence-kell/Dropbox/xval/iccat-bet",
                   "/home/laurence-kell/Dropbox/xval/iccat-yft"),"base"),
  file.path("/home/laurence-kell/Desktop/rfmo/iccat/sc-eco/2020/inputs/ss",c("sma/2019/run1",
                                                                             "bum/2018",
                                                                             "whm/2019/run6",
                                                                             "swon/2017/run1"))),
assessid=c("io-bet","io-yft","epo-bet","epo-yft","iccat-bet","iccat-yft","iccat-sma","iccat-bum","iccat-whm","iccat-swo"),
species=c("Thunnus obesus","Thunnus albacares",
          "Thunnus obesus","Thunnus albacares",
          "Thunnus obesus","Thunnus albacares",
          "Isurus oxyrinchus",
          "Makaira nigricans",
          "Kajikia albida",
          "Xiphias gladius"))
dat=ldply(dlply(ss,.(assessid,species), with, getSS(file)),getTs)

dt1=ddply(transform(cbind(subset(dat,assessid%in%ss[1:4,2]),qrtr=1:4),year=year-qrtr),.(assessid,species,year), with, 
             data.frame(year=(year[1]+3)/4,stock=stock[1],harvest=harvest[1],biomass=biomass[1],ssb=ssb[1],catch=sum(catch)))
ss=rbind.fill(dt1,subset(dat,!assessid%in%unique(dt1$assessid)))
trfmo=rbind.fill(ss,jb)
#trfmo=rbind(ddply(subset(trfmo,year<1000),.(assessid),transform, year=year+2018-max(year)),
#            subset(trfmo,year>1000))

nms=data.frame(
assessid=c("iccat-bet","epo-bet","io-bet",
           "iccat-yft","epo-yft","io-yft",
           "albsatl_iccat",
           "iccat-swo","swo_iotc","swo_natl","swo_satl","swomed_iccat",
           "iccat-bum","bum_iccat","bum_iotc",
           "iccat-whm","whm_iccat",
           "mls_iotc",
           "skj_iotc",
           "smanatl_iccat","iccat-sma",
           "bsh_iotc"),
species=c("Thunnus obesus","Thunnus obesus","Thunnus obesus",
          "Thunnus albacares","Thunnus albacares","Thunnus albacares",
          "Thunnus alalunga",
          "Xiphias gladius","Xiphias gladius","Xiphias gladius","Xiphias gladius","Xiphias gladius",
          "Makaira nigricans","Makaira nigricans","Makaira nigricans",
          "Kajikia albida","Kajikia albida",
          "Kajikia audax",
          "Katsuwonus pelamis",
          "Isurus oxyrinchus","Isurus oxyrinchus",
          "Prionace glauca"))
trfmo=rbind.fill(transform(ss,stockid=paste(assessid,"ss",sep="-")),
                 transform(jb,stockid=paste(assessid,"jabba",sep="-")))
trfmo=merge(trfmo[,-2],nms,by="assessid")
trfmo=ddply(trfmo,.(assessid), transform, year=year+ifelse(max(year),2018-max(year),0))
  
ggplot(trfmo)+
  geom_line(aes(year,stock))+
  facet_wrap(~assessid,scale="free")+
  theme_bw()+
  xlab("Year")+ylab(expression(B:B[MSY]))

save(trfmo,file=file.path(dirDat,"trfmo.RData"))
```


```{r}
load("file.path(dirDat,/ts.RData")
load(file.path(dirRes,"trfmo.RData"))

ts=rbind.fill(cbind("what"="RAM",merge(ts,stockid[,c("stockid","species")])),
              cbind("what"="RFMO",trfmo))[,c("what","assessid","species","year","stock","catch","harvest")]

ts=ddply(ts,.(what,assessid), with, {
  dat=merge(data.frame(year=min(year,na.rm=T):max(year,na.rm=T)),
            data.frame("species"=species,"year"=year,"stock"=stock,"catch"=catch,"harvest"=harvest),by="year",all.x=TRUE)})

ts=subset(ts,(!is.na(catch))|(!is.na(stock))) 
save(ts,file=file.path(dirDat,"ts.RData"))  
```


## Summary plots
```{r, ts-catch}
ggplot(ts)+  
  geom_path(aes(year,catch,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Catch")
```

**Figure `r iFig=iFig+1; iFig`** Timeseries of catch.


```{r, ts-stock}
ggplot(ts)+
  geom_path(aes(year,stock,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab(expression(SSB:B[MSY]))
```

**Figure `r iFig=iFig+1; iFig`** Timeseries of spawning stock biomass.

```{r, ts-harvest}
ggplot(ts)+
  geom_path(aes(year,harvest,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Harvest rate")
```

**Figure `r iFig=iFig+1; iFig`** Timeseries of harvest rate.

```{r, sh}
ggplot(ts)+  
  geom_path(aes(stock,harvest,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+ylab("Harvest Rate")+xlab(expression(SSB:B[MSY]))
```

**Figure `r iFig=iFig+1; iFig`** Trajectories of harvest rate v spawning stock biomass.

```{r, ts-sp, eval=FALSE}
sp=ddply(subset(ts,!is.na(ssb)|is.na(catch)),.(assessid,what), with, {data.frame(year=year[-length(ssb)],
                                           sp  =ssb[-1]-ssb[-length(ssb)]+catch[-length(ssb)],
                                           ssb =ssb[-length(ssb)])})

ggplot(sp)+
  geom_path(aes(year,sp,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Surplus Production")
```


```{r, trj-sp, eval=FALSE}
sp=ddply(subset(ts,!is.na(ssb)),.(assessid,what), with, {data.frame(year=year[-length(ssb)],
                                           sp  =ssb[-1]-ssb[-length(ssb)]+catch[-length(ssb)],
                                           ssb =ssb[-length(ssb)])})

ggplot(sp)+
  geom_path(aes(ssb,sp,col=what))+
  facet_wrap(~assessid,scale="free")+
  theme_bw(0)+xlab("Year")+ylab("Surplus Production")
```


```{r, msy}
names(stock)[3]="species"
bioparams=subset(bioparams,assessid%in%sid)
msy=subset(bioparams,bioid%in%c("SSBmsy-MT","MSY-MT","SSB0-MT"))
msy=cast(msy,stockid+assessid~bioid,value="biovalue")
names(msy)[3:5]=c("msy","K","bmsy")

msy=mutate(msy, msy=as.numeric(as.character( msy)),
                bmsy=as.numeric(as.character(bmsy)),
                hmsy=msy/bmsy)

msy$K=as.numeric(as.character(msy$K))
msy$shape=msy$bmsy/msy$K
msy=adply(msy, 1, function(x) data.frame(p=optimise(function(x,y) (y-(1/(1+x))^(1/x))^2,c(-0.9999,10),y=x$shape)$minimum))
msy=transform(msy,r=(1+p)*(msy/bmsy))

msy=subset(msy,!is.na(K))
msy=merge(msy[,-7],stockid[,c("stockid","species")])

save(msy,file=file.path(dirRes,"msy.RData"))  
```

```{r, lh}
ts=merge(ts,stockid[,c("stockid","species")])
lh=subset(fb,species%in%c(unique(ts$species),unique(trfmo$species)))

#ref=merge(msy,stockid,by="stockid")
lh[is.na(lh["lmat"]),"lmat"]=(lh[is.na(lh["lmat"]),"lmatmin"]+lh[is.na(lh["lmat"]),"lmatmax"])/2
lh=ddply(lh,.(species), with, data.frame(k   =mean(k,   na.rm=T),
                                         linf=mean(linf,na.rm=T),
                                         t0  =mean(t0,  na.rm=T),
                                         l50 =mean(lmat,na.rm=T),
                                         a50 =mean(amat,na.rm=T),
                                         a   =mean(a,   na.rm=T),
                                         b   =mean(b,   na.rm=T)))

lh$t0=pmin(-0.1,lh$t0)
lh[,-1][is.na(lh[,-1])]=NA

save(lh,file=file.path(dirRes,"lh.RData"))
```

```{r, kb}
kb=rbind(ddply(ts,   .(assessid),with, data.frame(stock=stock[year==max(year)],harvest=harvest[year==max(year)]))[,c("stock","harvest")],
         ddply(trfmo,.(assessid),with, data.frame(stock=stock[year==max(year)],harvest=harvest[year==max(year)]))[,c("stock","harvest")])

kobePhaseMar(kb,xlim=4,ylim=4)
```

**Figure `r iFig=iFig+1; iFig`** Kobe Phase plot for selected RAM Legacy database and tRFMO assessments.

```{r}
library(grid)

FAOPhaseMar(kb[,c("stock","harvest")],xlim=4,ylim=4)
```

**Figure `r iFig=iFig+1; iFig`** FAO plot for selected RAM Legacy database assessments and tRFMO assessments.

```{r}
msyNm=names(bioparams_values_views)[c(3:5,8,9,11,12,20)]
mgtNm=names(bioparams_values_views)[c(6,7,14,15,16,17)]
limNm=names(bioparams_values_views)[c(18,19,21,22,23,24)]
```

```{r, msy2, fig.width=8, fig.height=8}
ggpairs(transmute(msy,r=r,shape=bmsy/K))+theme_bw() 
```

**Figure `r iFig=iFig+1; iFig`** Relationship between population growth rate ($r$) and the ratio of $B_{MSY}:K$ (shape) based on selected data rich assessments.

```{r, pd}
load(file.path(dirRes,"lh.RData"))

lh$a[is.na(lh$a)]=0.002
lh$b[is.na(lh$b)]=3.0

pd=mydas:::popdyn(lhPar(as(lh[,c("linf","k","t0","a","b","l50")],"FLPar")))
dimnames(pd)$iter=lh$species

lh.low=lhPar(as(lh[,c("linf","k","t0","a","b","l50")],"FLPar"))

lh.low["m1"]=0.45
lh.low[ "s"]=0.8

pd.low=mydas:::popdyn(lhPar(lh.low))
dimnames(pd.low)$iter=lh$species

save(pd,pd.low,file=file.path(dirRes,"pd.RData"))  
```

```{r}
cpue  =subset(timeseries,assessid%in%unique(ts$assessid)) #&substr(tsid,1,4)=="cpue")
survey=subset(timeseries,assessid%in%unique(ts$assessid)&substr(tsid,1,4)=="surv")
```

```{r}
cpue =subset(timeseries_assessments_views,stockid%in%unique(ts$stockid)&!is.na(CPUE) )$CPUE
survB=subset(timeseries_assessments_views,stockid%in%unique(ts$stockid)&!is.na(survB))$survB
```

```{r}
taxa=merge(fao_taxa[[1]],fao_taxa[[2]])
```
